Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis.

### 2018-06-22 manuscript/index.Rmd
Update word count and imputation vignette

Section                   Word count          
--------                  --------------      ------------
Introduction              1060                Figures:
Materials and Methods     1603                5 (all colored)
Results                   1073
Discussion                1789                Tables:
Acknowledgements          88                  2
Total                     5613

>>>>

Section                   Word count          
--------                  --------------      ------------
Introduction              1060                Figures:
Materials and Methods     1695                5 (all colored)
Results                   1108
Discussion                1907                Tables:
Acknowledgements          88                  2
Total                     5858
